Lattice model

### 2017-03-30 oopsla17/lattice-model.tex

\begin{defn}{(\emph{Region})}
  \textit{Region} is the set of $N$ dimensional vector intervals defined as the
  smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \textit{Region}.
    \item If $R$ and $S$ are in \textit{Region}, then so are $R \cap S$ and $R
      \cup S$.
  \end{enumerate}
\end{defn}

\begin{prop}{}
  $(\textit{Region},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}
  Any sublattice of a distributive lattice is a distributive lattice. Power sets
  partially ordered with subset or equal to relation are distributive lattices.
  \textit{Region} is a subset of $\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}$ since
  all vector intervals are subsets of this power set and union and intersection
  cannot add an element that is not already in the powerset. Inductive
  definition also ensures that \textit{Region} is closed under these operations.
  Therefore, \textit{Region} is a distributive sublattice of
  $(\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}, \subseteq)$.
\end{proof}

@@

>>>>

\begin{defn}{(\emph{Region})}
  \region{N} is the set of $N$ dimensional vector intervals defined as
  the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}
  Any sublattice of a distributive lattice is a distributive lattice. Power sets
  partially ordered with subset or equal to relation are distributive lattices.
  \region{N} is a subset of $\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}$ since all
  vector intervals are subsets of this power set and union and intersection
  cannot add an element that is not already in the powerset.  Inductive
  definition also ensures that \region{N} is closed under these operations.
  Therefore, \region{N} is a distributive sublattice of
  $(\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}, \subseteq)$.
\end{proof}

@@

\begin{defn}{(Extended origin)}
  In the $N$ dimensional region space, ${(\interv{-1}{1}{\textsf{true}})}^N$ is
  said to be the extended origin.
\end{defn}

\begin{defn}{(Hearing)}
  A point, $p$, in \region{N} is said to \emph{talk to} the extended origin if
%
  \begin{enumerate}
    \item $p$ is in the extended origin;
    \item there are distinct indices $i$ and $j$ (between $1$ and $N$) such that
      $p_i$ is $-1$ to $1$ and there is a $p'$ that talks to the extended origin
      such that $p_j$ is ${p'}_j - 1$ or ${p'}_j + 1$ and for all other indices
      $k$, $p_k$ is ${p'}_k$;
    \item all immediate neighbours of $p$ that are no farther away from the
      extended origin than $p$ can talk to the extended origin.
  \end{enumerate}

  A set of points talk to the extended origin if all points in the set talk to
  the extended origin.
\end{defn}

\begin{lem}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ defines a superposition of hyper-rectangles each of which crosses
      the extended origin;
    \item $P$ talks to the extended origin
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ lies in \region{N}.
  \end{enumerate}
\end{lem}
